### 2016-05-11 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated structure names, README for hose stream report exp names

\begin{figure}[!ht]
% \begin{minipage}[b]{0.8\columnwidth}
% 	\begin{flushleft}
% 	\small
% 	\begin{tabular}[b]{cc}
%  	\toprule
%  	\textbf{Number} & \textbf{Event Description} \\
%  	\midrule
%  	1-3  & Burners ignited \\
%  	4	 & 2nd floor west double door opened \\
%  	5 	 & 1st floor west double door opened \\
%  	6	 & 1st floor east double door opened \\
%  	7 	 & 2nd floor east double door opened \\
%  	8-10  & Burners extinguished \\
% 	\bottomrule
% 	\end{tabular}
% 	\end{flushleft}
% \end{minipage}
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 		& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	(1) Corner burner on 					& 	9:05 			&	 3:45		\\
	(2) Middle burner on 					&   8:45	  		&	 3:55		\\
	(3) Center burner on 					&   8:15	  		&	 4:04		\\
	(4) 2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	(5) 1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	(6) 1st floor east double door opened 	&   15:45		  	&    10:00		\\
	(7) 2nd floor east double door opened	&   18:00		  	&    12:08		\\
	(8) PPV fan on 							&   19:10		  	&    14:01		\\
	(9) PPV fan off              			&   21:34		  	&    16:30		\\
	(8) Center burner off 					&   22:00		  	&    17:00		\\
	(9) Middle burner off 					&   22:00		  	&    17:00		\\
	(10) Corner burner off 					&   22:00		  	&    17:00		\\
	% doors were opened, fan was on after burners turned off
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
% \begin{minipage}[b]{0.8\columnwidth}
% 	\begin{flushleft}
% 	\small
% 	\begin{tabular}[b]{cc}
%  	\toprule
%  	\textbf{Number} & \textbf{Event Description} \\
%  	\midrule
%  	1-3  & Burners ignited \\
%  	4	 & Interior stairwell door opened \\
%  	5 	 & 1st floor west double door opened \\
%  	6	 & 2nd floor west double door opened \\
%  	7 	 & 2nd floor south exterior door opened \\
%  	8-10 & Burners extinguished \\
% 	\bottomrule
% 	\end{tabular}
% 	\end{flushleft}
% \end{minipage}
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	(1) Corner burner on 						& 	2:30 			&	 2:00		\\
	(2) Middle burner on 						&   2:45	  		&	 2:00		\\
	(3) Center burner on 						&   3:00	  		&	 2:00		\\
	(4) Interior stairwell door opened 			&   5:00	  		&    4:00		\\
	(5) 1st floor west double door opened 		&	7:00	  		&    6:11 	 	\\
	(6) 2nd floor west double door opened 		&   9:00		  	&    8:00		\\
	(7) 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	(8) PPV fan on 								&   13:00		  	&    12:00 		\\
	% (9) PPV fan off              				&   16:30		  	&    		\\
	(8) Center burner off 						&   15:00		  	&    14:00		\\
	(9) Middle burner off 						&   15:00		  	&    14:00		\\
	(10) Corner burner off 						&   15:00		  	&    14:00		\\
	% doors were opened, fan was on after burners turned off
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}[!ht]
% \begin{minipage}[b]{0.8\columnwidth}
% 	\begin{flushleft}
% 	\small
% 	\begin{tabular}[b]{cc}
%  	\toprule
%  	\textbf{Number} & \textbf{Event Description} \\
%  	\midrule
%  	1-3  & Burners ignited \\
%  	4	 & 2nd floor west double door opened \\
%  	5 	 & 1st floor west double door opened \\
%  	6	 & 1st floor east double door opened \\
%  	7 	 & 2nd floor east double door opened \\
%  	8-10  & Burners extinguished \\
% 	\bottomrule
% 	\end{tabular}
% 	\end{flushleft}
% \end{minipage}
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 		& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	(1) Corner burner on 					& 	9:05 			&	 3:45		\\
	(2) Middle burner on 					&   8:45	  		&	 3:55		\\
	(3) Center burner on 					&   8:15	  		&	 4:04		\\
	(4) 2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	(5) 1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	(6) 1st floor east double door opened 	&   15:45		  	&    10:00		\\
	(7) 2nd floor east double door opened	&   18:00		  	&    12:08		\\
	(8) PPV fan on 							&   19:10		  	&    14:01		\\
	(9) PPV fan off              			&   21:34		  	&    16:30		\\
	(10) Center burner off 					&   22:00		  	&    17:00		\\
	(11) Middle burner off 					&   22:00		  	&    17:00		\\
	(12) Corner burner off 					&   22:00		  	&    17:00		\\
	% doors were opened, fan was on after burners turned off
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
% \begin{minipage}[b]{0.8\columnwidth}
% 	\begin{flushleft}
% 	\small
% 	\begin{tabular}[b]{cc}
%  	\toprule
%  	\textbf{Number} & \textbf{Event Description} \\
%  	\midrule
%  	1-3  & Burners ignited \\
%  	4	 & Interior stairwell door opened \\
%  	5 	 & 1st floor west double door opened \\
%  	6	 & 2nd floor west double door opened \\
%  	7 	 & 2nd floor south exterior door opened \\
%  	8-10 & Burners extinguished \\
% 	\bottomrule
% 	\end{tabular}
% 	\end{flushleft}
% \end{minipage}
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	(1) Corner burner on 						& 	2:30 			&	 2:00		\\
	(2) Middle burner on 						&   2:45	  		&	 2:00		\\
	(3) Center burner on 						&   3:00	  		&	 2:00		\\
	(4) Interior stairwell door opened 			&   5:00	  		&    4:00		\\
	(5) 1st floor west double door opened 		&	7:00	  		&    6:11 	 	\\
	(6) 2nd floor west double door opened 		&   9:00		  	&    8:00		\\
	(7) 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	(8) PPV fan on 								&   13:00		  	&    12:00 		\\
	% (9) PPV fan off              				&   16:30		  	&    		\\
	(9) Center burner off 						&   15:00		  	&    14:00		\\
	(10) Middle burner off 						&   15:00		  	&    14:00		\\
	(11) Corner burner off 						&   15:00		  	&    14:00		\\
	% doors were opened, fan was on after burners turned off
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier
